Random Fibonacci Anyons Simulable via Covariant Action of Mapping Class Group

### 2014-09-02 about.tex
tweaks

Below bond-percolation threshold we expect to see clusters
of charges of size $O(log(n))$ with variance $O(log(log(n))$. CITATION

@@

@@

The mapping class group $MCG(D_n)$ acts on curve diagrams $f : L_n\to D_n$
via post-composition (left multiplication).
This action is transitive and XXX so we can identify an element of
$MCG(D_n)$ by its action on any curve $f:L_n\to D_n.$
See \cite{Dehornoy02}, chapter 6.

@@

\heading{Disjoint sum of two curve diagrams}

@@

We aim discretize the problem for software implementation.
Our first task is to characterize what happens to a curve
if we ``forget'' any braiding inside a sub-disc.
We adapt the Abramsky combinatorial description 
of the Temperly-Lieb algebra to our needs
(see \cite{Abramsky08}, section 6.) %Proposition 1.6).

@@

%Now we consider a tiling of the disc into subdiscs that are disjoint on
%their interiors.
We now consider a cellulation of a disc.
Concretely, we choose a regular $l$ by $l$ square tiling of a square region.

The holes $Q_n$ will always be contained within the interior of the
tiles.

@@

@@

Extraction of syndrome, PICTURE

Clustering of charges, CITE BravyiHaah

Multi-round

@@

Threshold appears at $t_{\mathrm{sim}}\simeq 0.125$

@@

\heading{Conclusion}

@@

>>>>

Below bond-percolation threshold we expect to see clusters
of charges of size $O(log(n))$ with variance $O(1)$ \cite{Bazant00}.

@@

XXX $\partial L\to \partial D$ XXX

@@

The mapping class group $MCG(D_n)$ acts on curve diagrams $f : L_n\to D_n$
via post-composition (left multiplication).
This action is transitive and XXX so we can identify an element of
$MCG(D_n)$ by its action on any curve $f:L_n\to D_n.$
See \cite{Dehornoy02}, chapter 6.
XXX $\partial L\to \partial D$ XXX

@@

@@

We aim to discretize the problem for software implementation.
Our first task is to characterize what happens to a curve
if we ``forget'' any braiding inside a sub-disc.
We adapt the Abramsky combinatorial description 
of the Temperly-Lieb algebra to our needs
(see \cite{Abramsky08}, section 6.) %Proposition 1.6).

@@

%Now we consider a tiling of the disc into subdiscs that are disjoint on
%their interiors.
We now consider a cellulation of a disc.
Concretely, we choose a regular $l$ by $l$ square tiling of a square region.
The holes $Q_n$ will always be contained within the interior of the
tiles.

@@

\begin{center}
\includegraphics[width=0.4\textwidth]{discrete-curve.eps}
\end{center}

@@

PICTURE

Extraction of syndrome

PICTURE

Multi-round
Clustering of charges, \cite{Brell13} \cite{Bravyi13}

Fail on big braid

@@

Threshold appears at $t_{\mathrm{sim}}\simeq 0.124 \pm 0.004$

Plot of computational power...

@@

\heading{Conclusion/Discussion}

@@

Yo to my bro's and homies
